---
title: "CSM Comparison to Grand mean"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---



```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

Packages <- c("tidyverse", "multcomp", "arm", "brglm", "kableExtra", "ggpubr", "RColorBrewer")
lapply(Packages, library, character.only = TRUE)

```


```{r Data_import, echo=FALSE, message=FALSE, warning=FALSE}

setwd("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/Manuscript/Therapeutic Innovation & Regulatory Science/Resubmission/5000 simulations")

#dir() %>% data.frame() %>% mutate(lm=grepl('lm', `.`)) %>% filter(lm==TRUE)
#################################################################################################################################
#################################################################################################################################
########################################### ALPHA ###############################################################################
#################################################################################################################################
#################################################################################################################################

##### Balanced
nparcomp_balanced_alpha <- read.csv2("lm_nparcomp balanced alpha_5000.csv")
ordinal_nparcomp_balanced_alpha <- read.csv2("nparcom ordinal alpha_5000_balanced.csv")

##### Unbalanced


nparcomp_unbalanced_alpha <- read.csv2("lm_nparcomp unbalanced alpha_5000.csv")
nparcomp_ordinal_unbalanced_alpha <- read.csv2("nparcom ordinal unbalanced alpha_5000.csv")







# xaxislabel=50
# yaxislabel=50
# titleyaxis=60
# titlexaxis=50
# points_size=20
# order_legend=52
# legend.text=40

# xaxislabel=70
# yaxislabel=70
# titleyaxis=90
# titlexaxis=80
# points_size=20
# order_legend=52
# legend.text=40


xaxislabel=100
yaxislabel=100
titleyaxis=130
titlexaxis=120
points_size=30
order_legend=52+30
legend.text=45

hline=3
```





```{r echo=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}



myPalette <- colorRampPalette(rev(brewer.pal(11, "Accent")))
sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(0,3.5), breaks=c(0.2,1.5,2.5),
                             name=expression(delta))


gg_nparcomp_alpha_balanced <- nparcomp_balanced_alpha %>% pivot_longer(names_to = "Method", values_to="est.alpha", c(est.alpha_lm, est.alpha_nparcomp)) %>% mutate(Method= case_when(Method== "est.alpha_lm" ~ "Linear Model", Method=="est.alpha_nparcomp"~"Non-parametric")) %>% 
  ggplot(aes(factor(n1, levels = c(3,5,10,20,40,50,80,100,200)), est.alpha))+theme_bw()+  geom_point(position=position_jitter(width=0,height=0), size=points_size)+
  theme(axis.text.x = element_text(angle=0) ) +geom_hline(yintercept=0.05,  linetype="solid", 
                                                           color = "red", size=hline)+theme(strip.text = element_text(size=19), 
                                                                                axis.text.x = element_text(size = xaxislabel),
                                                                                axis.text.y = element_text(size = yaxislabel))+ #ggtitle("Unbalanced")+
  scale_shape_manual(values=c(1:16), name=expression(bold(n[i] ~ "in deviating center")))+
  labs(y = expression(alpha))+
  theme(legend.title = element_text(size=legend.text+10), legend.text = element_text(size=legend.text+10), axis.title.y = element_text(size=30), axis.title.x = element_text(size=19))+
  #ggtitle("Continuous") +
  theme(plot.title = element_text(hjust = 0.5, size=30))+ geom_line(aes(group=Method, linetype=Method, color=Method), size=1.5)+ xlab(expression(bold(n[i] ~ "per center")))+theme(axis.title.y = element_text(size = titleyaxis), 
                                                               axis.title.x = element_text(size = titlexaxis), 
                                                               legend.position = "bottom")+  guides(linetype=guide_legend(keywidth = 13, keyheight = 10) )+
  guides(linetype=guide_legend(keywidth = 10, keyheight = 15,  title.theme = element_text(size = 110, face = "bold"), label.theme = element_text(size=110)))+
  geom_hline(yintercept=0.044,  linetype="dashed", color="blue", size=hline)+
  geom_hline(yintercept=0.056,  linetype="dashed", color="blue", size=hline)#+ scale_x_continuous(breaks =nparcomp_balanced_alpha$n1)#+facet_wrap(~Method)


gg_nparcomp_alpha_balanced


#setwd("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/graphs")
#ggexport(gg_nparcomp_alpha_balanced, filename = "nparcomp_alpha_balanced.png", width = 1000,   height = 800)



```



```{r echo=FALSE, fig.height=10, fig.width=14, message=FALSE, warning=FALSE}





####

gg_nparcomp_unbalanced_alpha <- nparcomp_unbalanced_alpha %>% pivot_longer(names_to = "Method", values_to="est.alpha", c(est.alpha_lm, est.alpha_nparcomp)) %>% mutate(Method= case_when(Method== "est.alpha_lm" ~ "Linear Model", Method=="est.alpha_nparcomp"~"Non-parametric")) %>% 
      mutate(n1=factor(n1, levels = factor(unique(sort(nparcomp_unbalanced_alpha$n1))) ), 
         n2=factor(n2, levels = factor(unique(sort(nparcomp_unbalanced_alpha$n2))) )) %>%  
  ggplot(aes(factor(n1, levels = c(6,10,20,40,80,100,160,200,400)), est.alpha))+theme_bw()+  geom_point(position=position_jitter(width=0,height=0), aes(shape=(n2), stroke=2), size=points_size)+
  theme(axis.text.x = element_text(angle=0) ) +geom_hline(yintercept=0.05, linetype="solid", 
                                                           color = "red", size=hline)+theme(strip.text = element_text(size=19), 
                                                                                axis.text.x = element_text(size = xaxislabel),
                                                                                axis.text.y = element_text(size = yaxislabel))+ #ggtitle("Unbalanced")+
  scale_shape_manual(values=c(1:16), name=expression(bold(n[i] ~ "in unbalanced center")))+
  labs(y = expression(alpha))+
  theme(legend.title = element_text(size=legend.text+40), legend.text = element_text(size=legend.text+40), axis.title.y = element_text(size=30))+
  ggtitle("") +
  theme(axis.title.x = element_text(size=19),plot.title = element_text(hjust = 0.5, size=30))+ geom_line(aes(group=Method, linetype=Method, color=Method), size=1.5)+theme(legend.position="bottom")+xlab(expression(bold(n[i] ~ "per center")))+#ggtitle("Continuous")
theme(axis.title.y = element_text(size = titleyaxis),  axis.title.x = element_text(size = titlexaxis))+theme(legend.spacing = unit(10, unit="cm"))+  guides(linetype=guide_legend(keywidth = 5, direction = "vertical") ) +
guides(color = FALSE) + geom_hline(yintercept=0.044,  linetype="dashed", color="blue", size=hline)+
  geom_hline(yintercept=0.056,  linetype="dashed", color="blue", size=hline)   #+   scale_x_continuous(breaks =nparcomp_unbalanced_alpha$n1)
#+facet_wrap(~Method)


#gg_nparcomp_unbalanced_alpha


#setwd("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/graphs")
#ggexport(gg_nparcomp_unbalanced_alpha, filename = "nparcomp_unbalanced_alpha.png", width = 1250,   height = 900)




```




```{r echo=FALSE, fig.height=10, fig.width=14, message=FALSE, warning=FALSE}


ordinal_nparcomp_balanced_alpha <-  ordinal_nparcomp_balanced_alpha %>% mutate(n=factor(n, levels = c("3", "5", "10", "20", "40", "50", 
                                                                                                              "80", "100", "200")))


gg_ordinal_alpha_balanced  <- ordinal_nparcomp_balanced_alpha %>%  ggplot(aes(n, est.alpha))+  
  geom_point(position=position_jitter(width=0.,height=0), size=points_size)+
  
  theme_bw()+
   theme(axis.text.x = element_text(angle=0, size = xaxislabel) , axis.text.y = element_text(size =yaxislabel),  axis.title.y = element_text(size =19), 
         axis.title.x =  element_text(size =19)) +
   geom_hline(yintercept=0.05, linetype="solid",   color = "red", size=hline)+ ylab("Type I error ")+ xlab(expression(bold(n[i] ~ "per center")))+
  scale_y_continuous(breaks=c(0.05,0.08,0.12,0.15,0.18, 0.20))+ guides( size = FALSE)+
    labs(y = expression(alpha))+
    theme(legend.title = element_text(size=legend.text+10), axis.title.y = element_text(size=30), legend.text = element_text(size=legend.text+10))+
  #ggtitle("Ordinal") +
  theme(plot.title = element_text(hjust = 0.5, size=30))+theme(axis.title.y = element_text(size = titleyaxis), 
                                                               axis.title.x = element_text(size = titlexaxis))+geom_line(aes(group=1), size=1.5)+
  geom_hline(yintercept=0.044,  linetype="dashed", color="blue", size=hline)+
  geom_hline(yintercept=0.056,  linetype="dashed", color="blue", size=hline)
 

#gg_ordinal_alpha_balanced 


#setwd("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/graphs")
#ggexport(gg_ordinal_alpha_balanced, filename = "ordinal_alpha_balanced.png", width = 1000,   height = 800)
 
 
```

#### **Unbalanced**
```{r echo=FALSE, fig.height=10, fig.width=14, message=FALSE, warning=FALSE}


 
 
nparcomp_ordinal_unbalanced_alpha <- nparcomp_ordinal_unbalanced_alpha %>% 
   mutate(n1=factor(n1, levels = factor(unique(sort(nparcomp_unbalanced_alpha$n1))) ), 
         n2=factor(n2, levels = factor(unique(sort(nparcomp_unbalanced_alpha$n2))) ))
  
gg_ordinal_alpha_unbalanced <- nparcomp_ordinal_unbalanced_alpha %>% mutate(est.alpha=as.numeric(as.character((est.alpha)))) %>% 
   ggplot(aes(n1, est.alpha))+theme_bw()+  geom_point(position=position_jitter(width=0.0,height=0), aes(shape=n2, stroke=2), size=points_size)+
    theme(axis.text.x = element_text(angle=0, size=xaxislabel), 
          axis.text.y = element_text(angle=0, size=yaxislabel)) +geom_hline(yintercept=0.05, linetype="solid", 
                            color = "red", size=hline)+theme(strip.text = element_text(size=19), 
                      axis.text.y = element_text(size = yaxislabel))+ #ggtitle("Unbalanced")+
    scale_shape_manual(values=c(1:16), name=expression(bold(n[i] ~ "in unbalanced center")))+ xlab(expression(bold(n[i] ~ "per center")))+
     theme( 
        legend.text = element_text(size = legend.text+30+10), 
        title=element_text(size=17))+
      labs(y = expression(alpha))+
    theme(legend.title = element_text(size=50+50), axis.title.y = element_text(size=30))+
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5, size=30))+theme(legend.position="bottom")+theme(axis.title.y = element_text(size = titleyaxis), 
                                                               axis.title.x = element_text(size = titlexaxis))+theme(legend.spacing = unit(10, unit="cm"))+geom_line(aes(group=1), size=1.5)+geom_hline(yintercept=0.044,  linetype="dashed", color="blue", size=hline)+
  geom_hline(yintercept=0.056,  linetype="dashed", color="blue", size=hline)#+ggtitle("Ordinal")
 
 
#gg_ordinal_alpha_unbalanced



#setwd("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/graphs")
#ggexport(gg_ordinal_alpha_unbalanced, filename = "ordinal_alpha_unbalanced.png", width = 1250,   height = 900)


```







## **Sum up1** {.tabset}


### **alpha**
```{r eval=FALSE, fig.height=20, fig.width=22, include=FALSE}

ls <- ls() %>% as.data.frame() %>% mutate(alpha=case_when(grepl('alpha', `.`) & grepl('gg', `.`) ~ "alpha", 
                                                    grepl('power', `.`) & grepl('gg', `.`) ~ "power" )   )

alpha <- ggarrange(



ggarrange(gg_nparcomp_alpha_balanced ,

        #gg_nparcomp_alpha_unbalanced ,
        gg_nparcomp_unbalanced_alpha,

          nrow=1,  #legend="bottom" ,
        labels=c("(C)", "(D)")  ,  font.label=list(color="black",size=order_legend)

    ) %>% annotate_figure( top = text_grob("Continuous",
               color = "red", face = "bold", size = 60)),




ggarrange(gg_ordinal_alpha_balanced ,

        gg_ordinal_alpha_unbalanced ,

          nrow=1 ,  #legend="bottom",
        labels=c("E", "F")  ,  font.label=list(color="black",size=order_legend)

    ) %>% annotate_figure( top = text_grob("Ordinal",
               color = "red", face = "bold", size = 60)),
nrow = 3

)
alpha


# 
# 
# tiff("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/up/alpha_tiff.tiff",   width=3500, height=1800, res=36)
# ggarrange(
# ggarrange(gg_binomial_alpha_balanced + theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")), 
#         
#         gg_binomial_alpha_unbalanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")) , 
#     
#        nrow=1,  legend="bottom" , 
#        labels=c("A", "B")  ,  font.label=list(color="black",size=order_legend) # , hjust = c(2,2)
#      
#     ) %>% annotate_figure( top = text_grob("Binomial", 
#                color = "red", face = "bold", size = 60)),
# 
# 
# 
# ggarrange(gg_nparcomp_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")), 
#         
#         #gg_nparcomp_alpha_unbalanced , 
#         gg_nparcomp_unbalanced_alpha+theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")),
#     
#           nrow=1,  #legend="bottom" ,
#         labels=c("C", "D")  ,  font.label=list(color="black",size=order_legend)
#      
#     ) %>% annotate_figure( top = text_grob("Continuous", 
#                color = "red", face = "bold", size = 60)),
# 
# 
# 
# 
# ggarrange(gg_ordinal_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")), 
#         
#         gg_ordinal_alpha_unbalanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold")), 
#     
#           nrow=1 ,  #legend="bottom", 
#         labels=c("E", "F")  ,  font.label=list(color="black",size=order_legend)
#      
#     ) %>% annotate_figure( top = text_grob("Ordinal", 
#                color = "red", face = "bold", size = 60)),
# nrow = 3
# 
# )
# dev.off()




# pdf("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/CSM simulation/results-graphs/dat_3/up/alpha1.pdf", 
#     width = 160, height = 80)

jpeg("C:/Users/FirasFneish/MS Forschungs- und Projektentwicklungs-gGmbH/MSFP-Statistik - Dokumente/CSM/Manuscript/Therapeutic Innovation & Regulatory Science/Resubmission/5000 simulations/alpha_jpeg_5000_caption.jpeg",
      res=50, width = 390, height = 300, units = "cm")


annotate_figure(
ggarrange(


ggarrange(gg_nparcomp_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
        
        #gg_nparcomp_alpha_unbalanced , 
        gg_nparcomp_unbalanced_alpha+theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")),
    
          nrow=1,  #legend="bottom" ,
        labels=c("C", "D")  ,  font.label=list(color="black",size=order_legend)
     
    ) %>% annotate_figure( top = text_grob("Continuous", 
               color = "black", face = "bold", size = 90)),




ggarrange(gg_ordinal_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
        
        gg_ordinal_alpha_unbalanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
    
          nrow=1 ,  #legend="bottom", 
        labels=c("E", "F")  ,  font.label=list(color="black",size=order_legend)
     
    ) %>% annotate_figure( top = text_grob("Ordinal", 
               color = "black", face = "bold", size = 90)),
nrow = 2

)
,


fig.lab = "The probability of falsely rejecting the null hypothesis for at least one center as a function of sample size for each method applied on relevant response outcome for balanced (left panel) and unbalanced designs (right panel).\n The nominal type I error rate (α=0.05) is shown as a horizontal line. Dotted blue lines indicate error margins for simulations with 5000 runs.\n Simulated type-I-errors falling outside [0.044; 0.056] indicate a significant deviation from the prespecified level alpha=0.05).",
 fig.lab.size=150, 
fig.lab.pos = c("bottom.left")


)
dev.off()



```


```{r}






ggarrange(


ggarrange(gg_nparcomp_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
        
        #gg_nparcomp_alpha_unbalanced , 
        gg_nparcomp_unbalanced_alpha+theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")),
    
          nrow=1,  #legend="bottom" ,
        labels=c("C", "D")  ,  font.label=list(color="black",size=order_legend)
     
    ) %>% annotate_figure( top = text_grob("Continuous", 
               color = "black", face = "bold", size = 90)),




ggarrange(gg_ordinal_alpha_balanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
        
        gg_ordinal_alpha_unbalanced +theme(axis.text.x = element_text(color = "black", face="bold"), axis.text.y= element_text(color = "black", face = "bold"), 
                                             legend.title = element_text(face = "bold"), legend.text = element_text(face = "bold"), axis.title.x = element_text(face = "bold"), axis.title.y = element_text(face = "bold")), 
    
          nrow=1 ,  #legend="bottom", 
        labels=c("E", "F")  ,  font.label=list(color="black",size=order_legend)
     
    ) %>% annotate_figure( top = text_grob("Ordinal", 
               color = "black", face = "bold", size = 90)),
nrow = 2

)




```

The probability of falsely rejecting the null hypothesis for at least one center as a function of sample size for each method applied on relevant response outcome for balanced (left panel) and unbalanced designs (right panel). The nominal type I error rate (alpha=0.05) is shown as a horizontal line. Dotted blue lines indicate error margins for simulations with 5000 runs. Simulated type-I-errors falling outside [0.044; 0.056] indicate a significant deviation from the prespecified level alpha=0.05).
